---
title: "Grades"
author: "Angelos Theodorakis"
date: "28/5/2020"
output: 
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,echo = FALSE,include=FALSE}
library(ggplot2) # We load some libraries.
library(dplyr)
```

### First we clean the data a bit and have a look at some statistics

```{r,echo=FALSE}
setwd("C:/Users/User/Desktop/Άγγελος/Μουσικών σπουδών")
data<-read.csv("Grades.csv",sep=";",header = TRUE)
data<-data[,-9] #Remove the last X column
data<-data[complete.cases(data), ] #Remove rows with NA's
data$Βαθμός<-as.numeric(data$Βαθμός)
mean(data$Βαθμός) # Grades mean 
median(data$Βαθμός) # Grades median 
data$ΕΤΟΣ<-as.factor(data$ΕΤΟΣ)
summary(data$ΕΤΟΣ) # Number of lessons we have passed each year
```

### Next, we will plot the number of lessons we have successfully passed, each year:

```{r,echo=FALSE}
ggplot(data, aes(x = factor(ΕΤΟΣ),fill=ΕΤΟΣ)) +  
  geom_bar(aes(y = (..count..))) +
  geom_text(stat='count', aes(label=..count..), vjust=-.3) +
  labs(title='Πλήθος Μαθημάτων ανα έτος', x='',y='Αριθμός μαθήματων')+
  theme(plot.title = element_text(hjust = 0.5),legend.position = "None")
```
  


```{r,echo=FALSE}
data$Εξάμηνο<-as.factor(data$Εξάμηνο)
summary(data$Εξάμηνο)
```

### Then, we will find the number of lessons we have successfully passed, according to the semester they belong to.

```{r,echo=FALSE}
ggplot(data, aes(x = factor(Εξάμηνο),fill=Εξάμηνο)) +  
  geom_bar(aes(y = (..count..))) +
  geom_text(stat='count', aes(label=..count..), vjust=-.3) +
  labs(title='Πλήθος Μαθημάτων κάθε εξαμήνου', x='Εξάμηνο',y='Πλήθος')+
  theme(plot.title = element_text(hjust = 0.5),legend.position = "None")
```

```{r,echo=FALSE}
data$Περίοδος <- droplevels(data$Περίοδος)
summary(data$Περίοδος)
```

### Below is the number of lessons per exam period:

```{r,echo=FALSE}
ggplot(data, aes(x = factor(Περίοδος),fill=Περίοδος)) +  
  geom_bar(aes(y = (..count..))) +
  geom_text(stat='count', aes(label=..count..), vjust=-.3) +
  labs(title='Πλήθος Μαθημάτων ανα εξεταστική περίοδο', x='Εξάμηνο',y='Πλήθος')+
  theme(plot.title = element_text(hjust = 0.5),legend.position = "None")
```

### We can also make some boxplots and tables regarding the grades for each year, and for each period:

```{r,echo=FALSE}
ggplot(data, aes(x=ΕΤΟΣ, y=Βαθμός, fill=ΕΤΟΣ)) +
  geom_boxplot()
table(data$ΕΤΟΣ,data$Βαθμός)
ggplot(data, aes(x=Περίοδος, y=Βαθμός, fill=Περίοδος)) +
  geom_boxplot()
table(data$Περίοδος,data$Βαθμός)
```

### Below is the number and percentage of lessons per grade:

```{r,echo=FALSE}
ggplot(data, aes(x = factor(Βαθμός),fill=factor(Βαθμός))) +  
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=-.3) +
  labs(title='Πλήθος Μαθημάτων ανα βαθμολογία', x='Βαθμός',y='Πλήθος')+
  theme(plot.title = element_text(hjust = 0.5),legend.position = "None")
  
ggplot(data, aes(x = factor(Βαθμός))) +  
  geom_bar(aes(y = (..count..)/sum(..count..), fill = factor(Βαθμός))) + 
  geom_text(aes( label = scales::percent((..count..)/sum(..count..)),
                 y=(..count..)/sum(..count..) ), stat= "count", vjust =-.3)+
  labs(title='Ποσοστό Μαθημάτων ανα βαθμολογία', x='Βαθμός',y='Ποσοστό')+
  theme(plot.title = element_text(hjust = 0.5),legend.position="none")
```

### Next, we have the same plot divided by each year:

```{r,echo=FALSE}
ggplot(data, aes(x = factor(Βαθμός),fill=factor(Βαθμός))) +  
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=-.3) +
  labs(title='Πλήθος Μαθημάτων ανα βαθμολογία', x='Βαθμός',y='Πλήθος')+
  theme(plot.title = element_text(hjust = 0.5),legend.position = "None")+
  facet_wrap(~factor(ΕΤΟΣ))
```

```{r,echo=FALSE,include=FALSE}
data$Βαρύτητα <- c(rep(1,nrow(data))) #sintelestis varititas
sum(data$Βαρύτητα * data$Βαθμός)/nrow(data) #vathmos ipologismenos me sintelesti varititas
```

### Now we will create a new column describing the category of the lessons (obligatory etc.) and then plot the number of lessons per category.

```{r,echo=FALSE}
data$Κατηγορία[c(32)]<- c("ΣΕΜΙΝΑΡΙΟ")
data$Κατηγορία[c(30)]<- c("ΕΠΙΛ.ΚΑΤΕΥΘΥΝΣΗΣ")
data$Κατηγορία[c(1:16,21:24,27)] <- c("ΥΠΟΧΡΕΩΤΙΚΟ")
data$Κατηγορία[c(17:20,25,26,28,29,31)]<- c("ΥΠ.ΚΑΤΕΥΘΥΝΣΗΣ")
data$Κατηγορία <-as.factor(data$Κατηγορία)

```

```{r,echo=FALSE}
ggplot(data, aes(x = factor(Κατηγορία),fill=Κατηγορία)) +  
  geom_bar(aes(y = (..count..))) +
  geom_text(stat='count', aes(label=..count..), vjust=-.3) +
  labs(title='Πλήθος Μαθημάτων ανα κατηγορία', x='',y='Πλήθος')+
  theme(plot.title = element_text(hjust = 0.5),legend.position = "None" )
```

### Now we will create some graphs showing our mean grade for each year.

```{r,echo=FALSE}
Grades<-data.frame(data %>%
                     group_by(ΕΤΟΣ) %>%
                     summarise(round(mean(Βαθμός),2)))
names(Grades)<-c("ΕΤΟΣ","Μ.Ο.")

tapply(data$Βαθμός,data$ΕΤΟΣ,FUN=mean)
plot(tapply(data$Βαθμός,data$ΕΤΟΣ,FUN=mean),ylim = c(5,10),type='b',xaxt='n',ylab="Βαθμός(Μ.Ο.)",xlab="Έτος",main="Μ.Ο. Μαθημάτων ανα Έτος")
text(Grades[,"ΕΤΟΣ"],Grades[,"Μ.Ο."],label=Grades[,"Μ.Ο."],col='blue',cex=.8,pos = 3)
axis(1, at=1:5, labels=levels(data$ΕΤΟΣ), cex.axis=1)
```

### Then, we do the same but this time for each category:

```{r,echo=FALSE}
GradesΚατηγορία<-data.frame(data %>%
                     group_by(Κατηγορία) %>%
                     summarise(round(mean(Βαθμός),2)))
names(GradesΚατηγορία)<-c("Κατηγορία","Μ.Ο.")

tapply(data$Βαθμός,data$Κατηγορία,FUN=mean)
plot(tapply(data$Βαθμός,data$Κατηγορία,FUN=mean),ylim = c(5,10),type='b',xaxt='n',ylab="Βαθμός(Μ.Ο.)",xlab="Κατηγορία",main="Μ.Ο. Μαθημάτων ανα Κατηγορία")
text(GradesΚατηγορία[,"Κατηγορία"],GradesΚατηγορία[,"Μ.Ο."],label=GradesΚατηγορία[,"Μ.Ο."],col='blue',cex=.8,pos = 3)
axis(1, at=1:4, labels=levels(data$Κατηγορία), cex.axis=0.8)
```

### Now for each exam period:

```{r,echo=FALSE}
GradesΠερίοδος<-data.frame(data %>%
                              group_by(Περίοδος) %>%
                              summarise(round(mean(Βαθμός),2)))
names(GradesΠερίοδος)<-c("Περίοδος","Μ.Ο.")

tapply(data$Βαθμός,data$Περίοδος,FUN=mean)
plot(tapply(data$Βαθμός,data$Περίοδος,FUN=mean),ylim = c(5,10),type='b',xaxt='n',ylab="Βαθμός(Μ.Ο.)",xlab="Περίοδος",main="Μ.Ο. Μαθημάτων ανα Περίοδο")
text(GradesΠερίοδος[,"Περίοδος"],GradesΠερίοδος[,"Μ.Ο."],label=GradesΠερίοδος[,"Μ.Ο."],col='blue',cex=.8,pos = 3)
axis(1, at=1:4, labels=levels(data$Περίοδος), cex.axis=0.8)
```

### Finally, the same for each semester:

```{r,echo=FALSE}
GradesΕξάμηνο<-data.frame(data %>%
                             group_by(Εξάμηνο) %>%
                             summarise(round(mean(Βαθμός),2)))
names(GradesΕξάμηνο)<-c("Εξάμηνο","Μ.Ο.")

tapply(data$Βαθμός,data$Εξάμηνο,FUN=mean)
plot(tapply(data$Βαθμός,data$Εξάμηνο,FUN=mean),ylim = c(5,10),type='b',xaxt='n',ylab="Βαθμός(Μ.Ο.)",xlab="Εξάμηνο",main="Μ.Ο. Μαθημάτων Εξαμήνου")
text(GradesΕξάμηνο[,"Εξάμηνο"],GradesΕξάμηνο[,"Μ.Ο."],label=GradesΕξάμηνο[,"Μ.Ο."],col='blue',cex=.8,pos = 3)
axis(1, at=1:7, labels=levels(data$Εξάμηνο), cex.axis=0.8)
```

```{r,echo=FALSE}
paste("Απομένουν ακόμα",52-nrow(data),"μαθήματα για πτυχίο!")
paste("Ο Γενικός Μέσος Όρος είναι",mean(data$Βαθμός))
```